A Short Guide to Anyons and Modular Functors

### 2016-09-25 guide.tex
commit edits

%space with these worldlines subtracted to be continuously

@@

When the above monodromy is constrained to two dimensions
we can no longer deform this process to the identity:
\begin{center}
\includegraphics[]{pic-monodromy2d.pdf}
\end{center}
and so in two dimensions we cannot expect a swap to square to the identity.
To see this more clearly,
we must examine the entire (2+1)-dimensional \emph{world-lines} of these particles.
For an example, here we show the world-lines of three particles undergoing an exchange and then
returning to their original positions:
\begin{center}
\includegraphics[]{pic-braid-worldlines.pdf}
\end{center}
Note that if we allow the particles to move in one extra
dimension then we can untangle these braided world lines.
%The question is, how has the wavefunction of the system
%changed from $t_0$ to $t_1$?
The question is now, what is the group that acts on the
state space from $t_0$ to $t_1$?
Examining the structure of these processes more closely,
we see that we can compose them by sequentially performing
two such braids, one after the other:
\begin{center}
\includegraphics[]{pic-braid-compose.pdf}
\end{center}
And, by ``reversing time'', we can undo the effect of
any braid:
\begin{center}
\includegraphics[]{pic-braid-inverse.pdf}
\end{center}
This shows that these processes do form a group,
known as the \emph{braid group.}
For $n$ particle worldlines we denote this group as $B_n.$
For identical particles this group acts as symmetries of the
state space:
%Now we would expect to see an action on the statespace $\F_n:$
$$
%    \Phi : B_n \to U(\F_n).
    \F : B_n \to U(V).
$$

>>>>

%space with these world-lines subtracted to be continuously

@@

When the above monodromy is constrained to two dimensions
we can no longer deform this process to the identity:
\begin{center}
\includegraphics[]{pic-monodromy2d.pdf}
\end{center}
and so in two dimensions we cannot expect a swap to square to the identity.
To see this more clearly,
we must examine the entire (2+1)-dimensional \emph{world-lines} of these particles.
For an example, here we show the world-lines of three particles undergoing an exchange and then
returning to their original positions:
\begin{center}
\includegraphics[]{pic-braid-worldlines.pdf}
\end{center}
Note that if we allow the particles to move in one extra
dimension then we can untangle these braided world lines.
%The question is, how has the wavefunction of the system
%changed from $t_0$ to $t_1$?
The question is now, what is the group that acts on the
state space from $t_0$ to $t_1$?
Examining the structure of these processes more closely,
we see that we can compose them by sequentially performing
two such braids, one after the other:
\begin{center}
\includegraphics[]{pic-braid-compose.pdf}
\end{center}
And, by ``reversing time'', we can undo the effect of
any braid:
\begin{center}
\includegraphics[]{pic-braid-inverse.pdf}
\end{center}
This shows that these processes do form a group,
known as the \emph{braid group.}
For $n$ particle world-lines we denote this group as $B_n.$
For identical particles this group acts as symmetries of the
state space:
%Now we would expect to see an action on the statespace $\F_n:$
$$
%    \Phi : B_n \to U(\F_n).
    \F : B_n \to U(V).
$$
